---
title: "Suitable places for electric charging stations in Erie County"
author: Nicholas Genco
subtitle: Subtitle here if desired
date: today
date-format: long
editor_options: 
  chunk_output_type: console
---

# Introduction

\[\~ 200 words\]

For my project, I want to look at where are the best places would be to put electric
charging stations. With electric vehicles becoming more popular, there is a growing demand for
charging stations and I want to know the best locations for them. Are streets, parking lots, homes
or sidewalks the best place to install them. I also would like to look at the specific locations that
they will go in to decide how many charging stations will be needed to fulfill the number of cars
that are present. Knowing how many cars on average fill up a parking lot is important in determining how many charging stations are required for that lot. The specific location I will be looking at for my project is the north eastern part of Erie County. I am looking at potentially identifying large parking lots (example Boulevard Consumer Plaza) as one of the ideal places to have charging stations. There are of course other large parking lots across Erie County but I didn't want to include every single one. I am also only looking at electric car charging stations as there are other fuel types out there that have their own charging stations or pumps for a specific type of vehicle. 

# Materials and methods

\[\~ 200 words\]

This first line of code shows the nearest electric charging stations across Erie County New York. There are certain areas in the county that have little to no electric charging stations including Kenmore, Lackawanna, areas south of Hamburg, Buffalo's East Side and areas east of Amherst and Williamsville. Areas that have a good amount of electric charging stations include parts of Downtown Buffalo, Cheektowaga, and Amherst. The second line of code represents the movable map that you can use to locate electric charging stations not just in Erie County but all over Western New York and if you were curious about another state or city, you could do that to. You can also change the type of fuel you want to locate such as Biodiesel, Compressed Natural Gas, Ethanol, Hydrogen, Liquefied Natural Gas, Propane, and Renewable Diesel. In the third line of code, I am using a pin to give the latitude and longitude of the location where I want electric charging stations. Since the map already has it's own pins as to where current charging stations exist, I decided to create my own pins in order to locate places where I believe electric charging stations are best suited for. 
```{r}
library(sf)
library(altfuelr)
library(tidycensus)
(nearest_stations(
  "ks60c5Uh2qpQzMoHhE3sdcYP68uJkspEFZOpd6Z2",
  latitude = 42.6975,
  longitude = -78.7476,
  radius = 300,
  params = nrel_params(fuel_type = "ELEC")
))
```
```{r}
options(tigris_use_cache = TRUE)
erie <- get_decennial(geography = "block", variables = income,
                      state = "NY", county = "Erie County", geometry = TRUE,
                      sumfile = "pl", cache_table=T) 
leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = electric,
                   color= "green",
                   radius = 300,
                   popup = ~paste("electric<br>", as.character(geometry))) %>%
```
```{r}
location_data <- data.frame(
  location_name = c("Boulevard Consumer Plaza"),
  longitude = c(-78.82234),
  latitude = c(42.99937),
)
# Load a base map (e.g., US states)

us_map <- map_data("state") 

# Create the map with a pin at the specified location

ggplot() +

  geom_polygon(data = us_map, aes(x = long, y = lat, group = group), fill = "gray", color = "black") + 

  geom_point(data = location_data, aes(x = longitude, y = latitude), color = "red", size = 3) + 

  coord_fixed() 
```


Data: This data shows us where current electric vehicle charging stations are located across the country. For my project though what I had to do was type in the area code for Erie County in order to have the map zoom into this area. It also gave me specific locations as to where a charging station is. An example of this is that there are two charging stations at Wegmans located at 675 Alberta Drive Amherst, NY 14226. An area that has a lot of charging stations is University at Buffalo's North Campus Jacobs B lot and that lot has 8 stations with 2 plugs each. 

You can do bullets like this:

-   The first most important thing
-   The second most important thing
-   The third most important thing

You can do numbers like this:

1.  The first most important thing
2.  The second most important thing
3.  The third most important thing

See <http://rmarkdown.rstudio.com/> for all the amazing things you can do.

Here's my first code chunk.



## Download and clean all required data



Add any additional processing steps here.

# Results

\[\~200 words\]

Tables and figures (maps and other graphics) are carefully planned to convey the results of your analysis. Intense exploration and evidence of many trials and failures. The author looked at the data in many different ways before coming to the final presentation of the data.

Show tables, plots, etc. and describe them.

```{r, fig.width=6, fig.height=3, fig.cap="Map of completely random data"}
m <- leaflet(data) %>% 
  addTiles() %>% 
  addCircleMarkers(~x, ~y, radius = ~size,color = ~as.factor(category)) %>% 
  addPopups(~x[2], ~y[2], "Random popup")
m  # a map with the default OSM tile layer
```

```{r}
data %>% 
  ggplot(aes(x=x,y=y,col=category))+
  geom_point()
```

### Dygraphs Example

```{r}
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") |> 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01")) 
```

# Conclusions

\[\~200 words\]

In conclusion, I believe that the places that would be the most suitable for electric charging stations are places that receive a lot of foot traffic such as the Boulevard Consumer Plaza since that area receives a lot of cars. Another possible location where I believe charging stations would be suitable are local schools and Universities since they are more likely to be concerned with their CO2 emissions. The University at Buffalo is a perfect example of a college who would want to have electric charging stations in their parking lots since they have a goal of making the campus carbon free. In order to do that they'll need people to drive electric vehicles and utilize the charging stations that are available in the parking lots. An area that I determined would not be ideal for charging stations are malls with two well known examples in Western New York being the Eastern Hills Mall and the Boulevard Mall since those are considered dead malls and don't receive a lot of visitors making it worthless even having them be located there. There were other places such as grocery stores parking lots, and gas stations that I considered as possible locations for charging stations but I ended up not going with those places. 

# References

https://developer.nrel.gov/docs/transportation/alt-fuel-stations-v1/
https://afdc.energy.gov/stations#/find/nearest?location=14226&fuel=ELEC

